\LARGE Performance Evaluation of Xenomai 3

### 2015-10-20 paper.tex
Change the author introduction by putting jserv and Che-Kang  togother\

\author{\large
{\bf Ching-Chun (Jim) Huang }\\
Department of Computer Science and Information Engineering, \\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
\vspace{8mm}
jserv$@$ccns.ncku.edu.tw\\
{\bf Chan-Hsiang Lin}\\
Department of Electrical and Electronic Engineering, National Taiwan University\\
No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)\\
\vspace{8mm}
r04943031$@$ntu.edu.tw\\
{\bf Che-Kang Wu}\\
Department of Computer Science and Information Engineering, \\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
\vspace{8mm}
an4006048$@$mail.ncku.edu.tw\\
}
\date{}

@@

\subsubsection{Kernel}
A Linux kernel that can be patched with PREEMPT\_RT, Xenomai 2 and Xenomai 3 is needed for the experiment (Xenomai 3 has to run on Linux kernel 3.10 or later versions). We selected Linux 3.14 for our experiment. In some cases when the patches couldn't be successfully applied on the kernel, we tried to resolve the conflicts manually.

\subsubsection{Kernel configuration [ipipe]}
Some of the kernel conﬁguration options may have an impact on real-time latencies. These options include all options under CPU Power Management, APM support, and Opportunistic sleep. Additionally, most debug options in Kernel hacking section lead to increased latencies. Those options are disabled before compilation.

@@

  The gravity values is the shortest time the platform needs to deliver an IRQ to a Xenomai interrupt handler,  a RTDM task running in kernel space, or a user-space task. It is used to differentiate timers on the target context they activate, among IRQ(handler), kernel and user threads, anticipating the next timer shot accordingly, so that such context is activated as close as possible to the ideal time. The gravity values can be set in the file `/proc/xenomai/latency` on Xenomai-2, `/proc/xenomai/clock/coreclk` on Xenomai-3 with root privilege. Furthermore, Xenomai-3 has an autotune function that runs a series of internal calibration tests for estimating the most appropriate gravity values for its real-time clock timer, retaining the final values.
Because Xenomai-2 doesn't have an autotune function and it has only one gravity value for all the 
coreclocks, we decided to manually tune all the coreclock values in both Xenomai-2 and Xenomai-3 to zero, so that we can later compare the results on the same basis.

>>>>

\author{\large
{\bf Ching-Chun (Jim) Huang, Che-Kang Wu }\\
Department of Computer Science and Information Engineering, \\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
\vspace{8mm}
jserv$@$ccns.ncku.edu.tw, an4006048$@$mail.ncku.edu.tw\\
{\bf Chan-Hsiang Lin}\\
Department of Electrical and Electronic Engineering, National Taiwan University\\
No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)\\
\vspace{8mm}
r04943031$@$ntu.edu.tw\\
}
\date{}

@@

\subsubsection{Kernel}
A Linux kernel that can be patched with PREEMPT\_RT, Xenomai 2 and Xenomai 3 is needed for the experiment (Xenomai 3 has to run on Linux kernel 3.10 or later versions). We selected Linux 3.18 for our experiment. In some cases when the patches couldn't be successfully applied on the kernel, we tried to resolve the conflicts manually.

\subsubsection{Kernel configuration [ipipe]}
Some of the kernel conﬁguration options may have an impact on real-time latencies. These options include Power Management, especially CPU frequency scaling, value of HZ, NUMA conﬁguration and so on. Additionally, most debug options (Kernel hacking section) lead to increased latencies. We disabled these config options before compilation.

@@

  The gravity values is the shortest time the platform needs to deliver an IRQ to a Xenomai interrupt handler,  a RTDM task running in kernel space, or a user-space task. It is used to differentiate timers on the target context they activate, among IRQ(handler), kernel and user threads, anticipating the next timer shot accordingly, so that such context is activated as close as possible to the ideal time. The gravity values can be set in the file \begin{verbatim}/proc/xenomai/latency on Xenomai-2, /proc/xenomai/clock/coreclk
\end{verbatim} on Xenomai-3 with root privilege. Furthermore, Xenomai-3 has an autotune function that runs a series of internal calibration tests for estimating the most appropriate gravity values for its real-time clock timer, retaining the final values.
Because Xenomai-2 doesn't have an autotune function and it has only one gravity value for all the 
coreclocks, we decided to manually tune all the coreclock values in both Xenomai-2 and Xenomai-3 to zero, so that we can later compare the results on the same basis.
